\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-08 paper/paper.tex
Minor fixes; final submission already done

%-------------------------------------------------------------------------------
\begin{filecontents}{\jobname.bib}
%-------------------------------------------------------------------------------
@Book{arpachiDusseau18:osbook,
author =       {Arpaci-Dusseau, Remzi H. and Arpaci-Dusseau Andrea C.},
title =        {Operating Systems: Three Easy Pieces},
publisher =    {Arpaci-Dusseau Books, LLC},
year =         2015,
edition =      {1.00},
note =         {\url{http://pages.cs.wisc.edu/~remzi/OSTEP/}}
}
@InProceedings{waldspurger02,
author =       {Waldspurger, Carl A.},
title =        {Memory resource management in {VMware ESX} server},
booktitle =    {USENIX Symposium on Operating System Design and
Implementation (OSDI)},
year =         2002,
pages =        {181--194},
note =         {\url{https://www.usenix.org/legacy/event/osdi02/tech/waldspurger/waldspurger.pdf}}}
\end{filecontents}

@@

{\fontsize{12}{15}\selectfont 
Although their work is not a research paper,
the TigerBeetle team has provided inspiration to Redstone in their work developing a testing system for their database.
This work heavily involved hastened testing of simulated distributed system faults.
However, a significant limiting factor in their work as compared to ours is that the simulator is compiled specifically for the software being tested.
While this setup works for their well-abstracted code that they can freely recompile to embed the simulation,
there are many, many more distributed systems in the real world that this form of simulation suits poorly at best.

@@

{\fontsize{12}{15}\selectfont 
Figure 1 provides a visual representation of the architecture powering Redstone.
The box marked config represents the configuration settings of the entire simulator (particularly settings that dictate probabilities of event occurences during simulation such as packet dropping). The region marked "simulator space" represents the simulator process,
for which system calls are re-routed to the syscall implementations specified for the simulator run.
Within the simulator process there are multiple “machines”,
representations of physical machines that, in production, would actually be different machines, and a root rng. The root rng represents the seed and alters program flow.
Each of these machine abstractions have their own simulated disk space.
Each machine abstraction is associated with a child process,
called a “replica”,
of the simulator process that runs the actual functionality expected of the individual machine,
working with the machine’s “files” (the in-memory storage mocked up by the simulator). Additionally, the replicas effectively mock their own files, file descriptor tables, their own clock scales/jitter, and their own list of sockets.

@@

@@

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{\jobname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

@@

{\fontsize{12}{15}\selectfont 
Although their work is not a research paper,
the TigerBeetle \cite{tigerbeetle} team has provided inspiration to Redstone in their work developing a testing system for their database.
This work heavily involved hastened testing of simulated distributed system faults.
However, a significant limiting factor in their work as compared to ours is that the simulator is compiled specifically for the software being tested.
While this setup works for their well-abstracted code that they can freely recompile to embed the simulation,
there are many, many more distributed systems in the real world that this form of simulation suits poorly at best.

@@

{\fontsize{12}{15}\selectfont 
Figure 1 provides a visual representation of the architecture powering Redstone.
The box marked config represents the configuration settings of the entire simulator (particularly settings that dictate probabilities of event occurences during simulation such as packet dropping). The region marked "simulator space" represents the simulator process,
for which system calls are re-routed to the syscall implementations specified for the simulator run.
Within the simulator process there are multiple “machines”,
representations of physical machines that, in production, would actually be different machines, and a root RNG. The root RNG represents the seed and alters program flow.
Each of these machine abstractions have their own simulated disk space.
Each machine abstraction is associated with a child process,
called a “replica”,
of the simulator process that runs the actual functionality expected of the individual machine,
working with the machine’s “files” (the in-memory storage mocked up by the simulator). Additionally, the replicas effectively mock their own files, file descriptor tables, their own clock scales/jitter, and their own list of sockets.

@@

{\fontsize{12}{15}\selectfont 
Redstone introduces a deterministic simulation testing framework for distributed systems,
intercepting system calls and injecting faults in all necessary subsystems,
including network, disk, and clocks, dependent on a seed.
We show that,
although we depend on a comparatively-slow \texttt{ptrace}-based design that introduces significant overhead,
we are able to both introduce faults and deterministically replicate failure conditions.

\section{\txtrsdust Works Consulted}

{\fontsize{12}{15}\selectfont 
\begin{itemize}
\item https://tigerbeetle.com/blog
\item https://jepsen.io/analyses
\item https://man7.org/linux/man-pages/man2/ptrace.2.html
\item https://www.man7.org/linux/man-pages/man8/ld.so.8.html
\item https://man7.org/linux/man-pages/man7/vdso.7.html
\end{itemize}

@@

%-------------------------------------------------------------------------------
% \bibliographystyle{plain}
% \bibliography{\jobname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
